Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
Update regional_typologies.qmd

---
title: "Formulating Regional Typologies"
author: "CIFOR-ICRAF Indonesia"
date: last-modified
date-format: "dddd MMM D, YYYY"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
    embed-resources: true
reference-location: document
editor: visual
---

@@

## Application of Typology in the Development Masterplan for Integrated Land and Seascape

@@

![Urban-rural typology for NUTS level 3 regions](image/nuts.png){height="400"}
:::

@@

![Global Food Security Index](image/gfsi.png){height="400"}
:::
:::

@@

### A sample of ready-to-process data

### PCA Summary

### K-means cluster
:::

@@

@@

| Cluster | Name            | Total sub district | Area (ha) | \% Area |
|---------|-----------------|--------------------|-----------|---------|
| 1       | Islands         | 17                 | 126,847   | 3%      |
| 2       | Sub-rural areas | 65                 | 1,588,345 | 35%     |
| 3       | Urban areas     | 36                 | 145,226   | 3%      |
| 4       | Sub-urban areas | 111                | 1,162,856 | 26%     |
| 5       | Rural areas     | 77                 | 1,414,487 | 31%     |

| Cluster | Name            | Families | \% Families | Families density (KK/ha) |
|---------|-----------------|----------|-------------|--------------------------|
| 1       | Islands         | 67,717   | 0.03        | 53%                      |
| 2       | Sub-rural areas | 457,271  | 0.19        | 29%                      |
| 3       | Urban areas     | 561,495  | 0.24        | 387%                     |
| 4       | Sub-urban areas | 994,481  | 0.42        | 86%                      |
| 5       | Rural areas     | 261,832  | 0.11        | 19%                      |
:::

>>>>

---
title: "Formulating Regional Typologies"
author: "CIFOR-ICRAF Indonesia"
date: last-modified
date-format: "dddd MMM D, YYYY"
project:
  type: website
  output-dir: docs
format: 
  revealjs:
    theme: simple
    scrollable: true
reference-location: document
editor: visual
---

@@

## Application of Typology in the Development Masterplan for Integrated Land and Seascape {.smaller}

@@

[![Urban-rural typology for NUTS level 3 regions](image/nuts.png){height="400" fig-align="center"}](https://ec.europa.eu/eurostat/cache/RCI/#?vis=urbanrural.urb_typology&lang=en)
:::

@@

[![Global Food Security Index](image/gfsi.png){height="400" fig-align="center"}](https://impact.economist.com/sustainability/project/food-security-index/explore-countries)
:::
:::

@@

### A sample of ready-to-process data
```{r a sample of data }
#| warning: false
#| message: false
```

### PCA Summary
```{r Map}
#| warning: false
#| message: false
```

### K-means cluster
```{r K-means cluster}
#| warning: false
#| message: false
```
:::

@@

::: {.panel-tabset style="font-size:16px"}
### Map
```{r Map}
#| warning: false
#| message: false
library(plotly)
library(leaflet)
library(sf)
library(dplyr)

clusters_sulsel <- st_read("data/tipologi_5_kelas_sulsel.shp" , quiet = TRUE)
cluster_lookup <- readr::read_csv("data/cluster_names.csv")

# Constructing the label string first
clusters_sulsel$label_content <- with(
  clusters_sulsel,
  paste0(
    "<strong>Kabupaten:</strong> ",
    nmkab,
    "<br>",
    "<strong>Kecamatan:</strong> ",
    nmkec,
    "<br>",
    "<strong>Cluster:</strong> ",
    cluster
  )
) |> lapply(htmltools::HTML)

clusters_sulsel_with_name <- clusters_sulsel |> right_join(cluster_lookup, by = "cluster")

pal <-
  colorFactor(palette = "Set1", domain = clusters_sulsel_with_name$name)

# Create the leaflet map with HTML-rendered labels
leaflet(clusters_sulsel_with_name) |>
  addProviderTiles(providers$OpenStreetMap) |>
  addPolygons(
    fillColor = ~ pal(name),
    weight = 0.5,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = ~ label_content,
    labelOptions = labelOptions(noHide = FALSE,
                                direction = 'auto')
  ) |>
  addLegend(pal = pal,
            values = ~ name,
            title = "Typology")

```

```{r komposisi kecamatan}
#| warning: false
#| message: false
source("R/functions.R")
intisari_desk_kec <- readr::read_csv("data/interpretasi_tipologi_sulsel.csv") |> 
  dplyr::mutate(`Kepadatan RT` = `Luas (Ha)`/`Rumah Tangga`)

fig_luas <- intisari_desk_kec |> 
  filter(Nama != "Total") |> 
  plot_ly(labels = ~Nama, values = ~`Luas (Ha)`) |> 
  add_pie(hole = 0.6) |> 
  layout(title = "Area Composition (Ha)",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

# Show the plot
fig_luas
```

```{r donat RT}
# Create the plot for Jumlah RT
fig_RT <- intisari_desk_kec |> 
  filter(Nama != "Total") |> 
  plot_ly(labels = ~Nama, values = ~`Rumah Tangga`) |> 
  add_pie(hole = 0.6) |> 
  layout(title = "Number of Households",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

# Show the plot
fig_RT
```

@@

:::
